Quantitative neuroimaging with ANTs

### 2017-04-24 asnr2017.tex
ENH:  ASNR 2017

\documentclass[ignorenonframetext,]{beamer}
\setbeamertemplate{caption}[numbered]
\setbeamertemplate{caption label separator}{: }
\setbeamercolor{caption name}{fg=normal text.fg}
\beamertemplatenavigationsymbolsempty
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
\usetheme{AnnArbor}
\usecolortheme{dolphin}
\usefonttheme{professionalfonts}
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\newif\ifbibliography
\usepackage{color}
\usepackage{fancyvrb}
\newcommand{\VerbBar}{|}
\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
% Add ',fontsize=\small' for more characters per line
\usepackage{framed}
\definecolor{shadecolor}{RGB}{248,248,248}
\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{{#1}}}}
\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{{#1}}}
\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{{#1}}}
\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{{#1}}}
\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{{#1}}}
\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{{#1}}}
\newcommand{\CharTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{{#1}}}
\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{{#1}}}
\newcommand{\StringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{{#1}}}
\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{{#1}}}
\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{{#1}}}
\newcommand{\ImportTok}[1]{{#1}}
\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{{#1}}}}
\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{{#1}}}}}
\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{{#1}}}}}
\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{{#1}}}}}
\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{{#1}}}
\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{{#1}}}
\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{{#1}}}
\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{{#1}}}}
\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{{#1}}}}
\newcommand{\BuiltInTok}[1]{{#1}}
\newcommand{\ExtensionTok}[1]{{#1}}
\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{{#1}}}}
\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.77,0.63,0.00}{{#1}}}
\newcommand{\RegionMarkerTok}[1]{{#1}}
\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{{#1}}}}}
\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{{#1}}}}}
\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.94,0.16,0.16}{{#1}}}
\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.64,0.00,0.00}{\textbf{{#1}}}}
\newcommand{\NormalTok}[1]{{#1}}
\usepackage{longtable,booktabs}
\usepackage{caption}
% These lines are needed to make table captions work with longtable:
\makeatletter
\def\fnum@table{\tablename~\thetable}
\makeatother
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight0.8\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}

@@

\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}

@@

\title{``Dr.~Tustison (UVA) presentation''}
\author{Nick Tustison}
\date{}

@@

\section{Developers and
collaborators}\label{developers-and-collaborators}

\begin{frame}{Founders: Brian and Nick}

\includegraphics{./figures/brian_and_nick.png}

@@

\includegraphics{./figures/antsCollaborators2.png}

\(+\) \href{http://neuro.debian.net/pkgs/ants.html}{neurodebian},
\href{http://www.slicer.org/}{slicer},
\href{https://github.com/BRAINSia/BRAINSTools}{brainsfit},
\href{http://nipy.sourceforge.net/nipype/}{nipype},
\href{http://www.itk.org}{itk} and more \ldots{}

@@

\section{Why would you care?}\label{why-would-you-care}

\begin{frame}{``Free beer''}

\includegraphics{./licenses/figures/freebeerfreespeech.jpg}

@@

\begin{frame}{Software for medical image analysis}

\begin{itemize}
\item
  \href{http://fsl.fmrib.ox.ac.uk/fsldownloads/}{FSL}
\item
  \href{http://www.fil.ion.ucl.ac.uk/spm/software/}{SPM}
\item
  \href{http://www.fil.ion.ucl.ac.uk/spm/software/}{FreeSurfer}
\item
  \href{http://mipav.cit.nih.gov}{MIPAV}
\item
  \href{https://afni.nimh.nih.gov/afni}{AFNI}
\item
  Slicer, Elastix, SimpleITK, ANTs \(\longleftrightarrow\)
  \href{http://www.itk.org}{Insight Toolkit}
\item
  Many more at \href{http://idoimaging.com}{idoimaging.com}
\end{itemize}

@@

\section{ANTs lineage}\label{ants-lineage}

\begin{frame}{Image mapping and perception: 1877}

Francis Galton: \emph{Can we see criminality in the face?}

\includegraphics{./figures/galton.png}

\emph{What about syphilis, mental illness?}

\begin{frame}{Speaking of criminality\ldots{}}

\emph{Can we say anything about the U.S. Congress?}

\includegraphics{./background/figures/congressPersons.png}

\textbf{Maybe they should have used
\href{https://github.com/ntustison/CongressionalFaceTemplates}{ANTs}?}

\begin{frame}{Image mapping \& biology: 1917}

D'Arcy Thompson: \emph{Comparison of related forms}

\includegraphics{./figures/dthompson.png} --\textgreater{}

\begin{frame}{Image mapping \& biology: Current}

 \emph{Look where we are now!}
\includegraphics{./background/figures/r16xr85.png}

\section{Competitions}\label{competitions}

\begin{frame}{Algorithmic fight club}

\includegraphics{./competitions/figures/fightclub.jpg}

@@

\section{Major ANTs utilities}\label{major-ants-utilities}

\begin{frame}{Donoho?}

 \emph{``Papers are just advertisements for the science.''}

\begin{frame}{Neuro tools}

\includegraphics{./tools/figures/coreANtsToolsNeuro.png}

\begin{frame}{Pulmonary tools}

\includegraphics{./tools/figures/coreANtsToolsLung.png}

\begin{frame}{Symmetric Normalization (SyN)}

\(\int_{t=0}^{0.5} \left(\|\mathbf{v}_1(x,t)\|_L^2 + \|\mathbf{v}_2(x,t)\|_L^2\right)dt + \|I\left(\phi_1(x,0.5)\right) - J_i\left(\phi_2(x,0.5)\right)\|^2\)

\includegraphics{./papers/figures/fishes.png}

--\textgreater{}

NOtes: * Previously discussed Brians work * The variant most widely used
--\textgreater{}

\begin{frame}{Diffeomoprhisms: differentiable map with diff. inverse}

\includegraphics{./figures/highresdiffeos.jpg}

\begin{frame}{Diffeomorphisms: image parameterization in a metric space}

\includegraphics{./figures/shape_appearance.png}

\begin{frame}{Beyond original SyN}

\includegraphics{./papers/figures/Frontiers_ITK.png}

\includegraphics{./papers/figures/Frontiers_BSplineSyN.png}

\begin{frame}[fragile]{\texttt{antsRegistration}}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{$ }\KeywordTok{antsRegistration} \NormalTok{--help}

\KeywordTok{COMMAND}\NormalTok{:}
     \KeywordTok{antsRegistration}
          \KeywordTok{This} \NormalTok{program is a user-level registration application meant to utilize}
          \KeywordTok{ITKv4-only} \NormalTok{classes. The user can specify any number of }\StringTok{"stages"} \NormalTok{where a stage}
          \KeywordTok{consists} \NormalTok{of a transform}\KeywordTok{;} \KeywordTok{an} \NormalTok{image metric}\KeywordTok{;} \KeywordTok{and} \NormalTok{iterations, shrink factors, and}
          \KeywordTok{smoothing} \NormalTok{sigmas for each level.Note that dimensionality, metric, transform,}
          \KeywordTok{output}\NormalTok{, convergence, shrink-factors and smoothing-sigmas parameters are}
          \KeywordTok{mandatory.}

\KeywordTok{OPTIONS}\NormalTok{:}
     \KeywordTok{--version}
          \KeywordTok{Get} \NormalTok{Version Information.}

     \KeywordTok{-d}\NormalTok{, --dimensionality 2/3}
          \KeywordTok{This} \NormalTok{option forces the image to be treated as a specified-dimensional image. If}
          \KeywordTok{not} \NormalTok{specified, we try to infer the dimensionality from the input image.}

     \KeywordTok{-o}\NormalTok{, --output outputTransformPrefix}
                  \NormalTok{[}\KeywordTok{outputTransformPrefix}\NormalTok{,}\KeywordTok{<}\NormalTok{outputWarpedImage}\KeywordTok{>}\NormalTok{,}\KeywordTok{<}\NormalTok{outputInverseWarpedImage}\KeywordTok{>}\NormalTok{]}
          \KeywordTok{Specify} \NormalTok{the output transform prefix (output format is .nii.gz )}\KeywordTok{.} \KeywordTok{Optionally}\NormalTok{, one}
          \KeywordTok{can} \NormalTok{choose to warp the moving image to the fixed space and, if the inverse}
          \KeywordTok{transform} \NormalTok{exists, one can also output the warped fixed image. Note that only the}
          \KeywordTok{images} \NormalTok{specified in the first metric call are warped. Use antsApplyTransforms to}
          \KeywordTok{warp} \NormalTok{other images using the resultant transform(s)}\KeywordTok{.}

     \KeywordTok{-j}\NormalTok{, --save-state saveSateAsTransform}
          \KeywordTok{Specify} \NormalTok{the output file for the current state of the registration. The state}
          \KeywordTok{file} \NormalTok{is written to an hdf5 composite file. It is specially usefull if we want to}
          \KeywordTok{save} \NormalTok{the current state of a SyN registration to the disk, so we can load and}
          \KeywordTok{restore} \NormalTok{that later to continue the next registration process directly started}
          \KeywordTok{from} \NormalTok{the last saved state. The output file of this flag is the same as the}
          \KeywordTok{write-composite-transform}\NormalTok{, unless the last transform is a SyN transform. In that}
          \KeywordTok{case}\NormalTok{, the inverse displacement field of the SyN transform is also added to the}
          \NormalTok{output composite transform. Again notice that this file cannot be treated as a}
          \NormalTok{transform, and restore-state option must be used to load the written file by}
          \NormalTok{this flag.}

     \NormalTok{-k, --restore-state restoreStateAsATransform}
          \NormalTok{Specify the initial state of the registration which get immediately used to}
          \NormalTok{directly initialize the registration process. The flag is mutually exclusive}
          \NormalTok{with other intialization flags.If this flag is used, none of the}
          \NormalTok{initial-moving-transform and initial-fixed-transform cannot be used.}

     \NormalTok{-a, --write-composite-transform 1/(0)}
          \NormalTok{Boolean specifying whether or not the composite transform (and its inverse, if}
          \NormalTok{it exists) should be written to an hdf5 composite file. This is false by default}
          \NormalTok{so that only the transform for each stage is written to file.}
          \NormalTok{<VALUES>: 0}

     \NormalTok{-p, --print-similarity-measure-interval <unsignedIntegerValue>}
          \NormalTok{Prints out the CC similarity metric measure between the full-size input fixed}
          \NormalTok{and the transformed moving images at each iteration a value of 0 (the default)}
          \NormalTok{indicates that the full scale computation should not take placeany value greater}
          \NormalTok{than 0 represents the interval of full scale metric computation.}
          \NormalTok{<VALUES>: 0}

     \NormalTok{-v, --write-interval-volumes <unsignedIntegerValue>}
          \NormalTok{Writes out the output volume at each iteration. It helps to present the}
          \NormalTok{registration process as a short movie a value of 0 (the default) indicates that}
          \NormalTok{this option should not take placeany value greater than 0 represents the}
          \NormalTok{interval between the iterations which outputs are written to the disk.}
          \NormalTok{<VALUES>: 0}

     \NormalTok{-z, --collapse-output-transforms (1)/0}
          \NormalTok{Collapse output transforms. Specifically, enabling this option combines all}
          \NormalTok{adjacent transforms wherepossible. All adjacent linear transforms are written to}
          \NormalTok{disk}\KeywordTok{ in} \NormalTok{the forman itk affine transform }\KeywordTok{(}\NormalTok{called xxxGenericAffine.mat}\KeywordTok{).}
          \KeywordTok{Similarly}\NormalTok{, all adjacent displacement field transforms are combined when written}
          \KeywordTok{to} \NormalTok{disk (e.g. xxxWarp.nii.gz and xxxInverseWarp.nii.gz (if available))}\KeywordTok{.Also}\NormalTok{, an}
          \KeywordTok{output} \NormalTok{composite transform including the collapsed transforms is written to the}
          \KeywordTok{disk} \NormalTok{(called outputCollapsed(Inverse)}\KeywordTok{Composite}\NormalTok{)}\KeywordTok{.}
          \KeywordTok{<VALUES>}\NormalTok{: 1}

     \KeywordTok{-i}\NormalTok{, --initialize-transforms-per-stage (1)}\KeywordTok{/0}
          \KeywordTok{Initialize} \NormalTok{linear transforms from the previous stage. By enabling this option,}
          \KeywordTok{the} \NormalTok{current linear stage transform is directly intialized from the previous}
          \KeywordTok{stage}\StringTok{'s linear transform; this allows multiple linear stages to be run where}
\StringTok{          each stage directly updates the estimated linear transform from the previous}
\StringTok{          stage. (e.g. Translation -> Rigid -> Affine).}
\StringTok{          <VALUES>: 0}

\StringTok{     -n, --interpolation Linear}
\StringTok{                         NearestNeighbor}
\StringTok{                         MultiLabel[<sigma=imageSpacing>,<alpha=4.0>]}
\StringTok{                         Gaussian[<sigma=imageSpacing>,<alpha=1.0>]}
\StringTok{                         BSpline[<order=3>]}
\StringTok{                         CosineWindowedSinc}
\StringTok{                         WelchWindowedSinc}
\StringTok{                         HammingWindowedSinc}
\StringTok{                         LanczosWindowedSinc}
\StringTok{          Several interpolation options are available in ITK. These have all been made}
\StringTok{          available. Currently the interpolator choice is only used to warp (and possibly}
\StringTok{          inverse warp) the final output image(s).}

\StringTok{     -g, --restrict-deformation PxQxR}
\StringTok{          This option allows the user to restrict the optimization of the displacement}
\StringTok{          field, translation, rigid or affine transform on a per-component basis. For}
\StringTok{          example, if one wants to limit the deformation or rotation of 3-D volume to the}
\StringTok{          first two dimensions, this is possible by specifying a weight vector of '}\NormalTok{1x1x0}\StringTok{'}
\StringTok{          for a deformation field or '}\NormalTok{1x1x0x1x1x0}\StringTok{' for a rigid}
\StringTok{          transformation.Low-dimensional restriction only works if there are no preceding}
\StringTok{          transformations.}

\StringTok{     -q, --initial-fixed-transform initialTransform}
\StringTok{                                   [initialTransform,<useInverse>]}
\StringTok{                                   [fixedImage,movingImage,initializationFeature]}
\StringTok{          Specify the initial fixed transform(s) which get immediately incorporated into}
\StringTok{          the composite transform. The order of the transforms is stack-esque in that the}
\StringTok{          last transform specified on the command line is the first to be applied. In}
\StringTok{          addition to initialization with ITK transforms, the user can perform an initial}
\StringTok{          translation alignment by specifying the fixed and moving images and selecting an}
\StringTok{          initialization feature. These features include using the geometric center of the}
\StringTok{          images (=0), the image intensities (=1), or the origin of the images (=2).}

\StringTok{     -r, --initial-moving-transform initialTransform}
\StringTok{                                    [initialTransform,<useInverse>]}
\StringTok{                                    [fixedImage,movingImage,initializationFeature]}
\StringTok{          Specify the initial moving transform(s) which get immediately incorporated into}
\StringTok{          the composite transform. The order of the transforms is stack-esque in that the}
\StringTok{          last transform specified on the command line is the first to be applied. In}
\StringTok{          addition to initialization with ITK transforms, the user can perform an initial}
\StringTok{          translation alignment by specifying the fixed and moving images and selecting an}
\StringTok{          initialization feature. These features include using the geometric center of the}
\StringTok{          images (=0), the image intensities (=1), or the origin of the images (=2).}

\StringTok{     -m, --metric CC[fixedImage,movingImage,metricWeight,radius,<samplingStrategy=\{None,Regular,Random\}>,<samplingPercentage=[0,1]>]}
\StringTok{                  MI[fixedImage,movingImage,metricWeight,numberOfBins,<samplingStrategy=\{None,Regular,Random\}>,<samplingPercentage=[0,1]>]}
\StringTok{                  Mattes[fixedImage,movingImage,metricWeight,numberOfBins,<samplingStrategy=\{None,Regular,Random\}>,<samplingPercentage=[0,1]>]}
\StringTok{                  MeanSquares[fixedImage,movingImage,metricWeight,radius=NA,<samplingStrategy=\{None,Regular,Random\}>,<samplingPercentage=[0,1]>]}
\StringTok{                  Demons[fixedImage,movingImage,metricWeight,radius=NA,<samplingStrategy=\{None,Regular,Random\}>,<samplingPercentage=[0,1]>]}
\StringTok{                  GC[fixedImage,movingImage,metricWeight,radius=NA,<samplingStrategy=\{None,Regular,Random\}>,<samplingPercentage=[0,1]>]}
\StringTok{                  ICP[fixedPointSet,movingPointSet,metricWeight,<samplingPercentage=[0,1]>,<boundaryPointsOnly=0>]}
\StringTok{                  PSE[fixedPointSet,movingPointSet,metricWeight,<samplingPercentage=[0,1]>,<boundaryPointsOnly=0>,<pointSetSigma=1>,<kNeighborhood=50>]}
\StringTok{                  JHCT[fixedPointSet,movingPointSet,metricWeight,<samplingPercentage=[0,1]>,<boundaryPointsOnly=0>,<pointSetSigma=1>,<kNeighborhood=50>,<alpha=1.1>,<useAnisotropicCovariances=1>]}
\StringTok{                  IGDM[fixedImage,movingImage,metricWeight,fixedMask,movingMask,<neighborhoodRadius=0x0>,<intensitySigma=0>,<distanceSigma=0>,<kNeighborhood=1>,<gradientSigma=1>]}
\StringTok{          These image metrics are available--- CC: ANTS neighborhood cross correlation,}
\StringTok{          MI: Mutual information, Demons: (Thirion), MeanSquares, and GC: Global}
\StringTok{          Correlation. The "metricWeight" variable is used to modulate the per stage}
\StringTok{          weighting of the metrics. The metrics can also employ a sampling strategy}
\StringTok{          defined by a sampling percentage. The sampling strategy defaults to '}\NormalTok{None}\StringTok{' (aka}
\StringTok{          a dense sampling of one sample per voxel), otherwise it defines a point set over}
\StringTok{          which to optimize the metric. The point set can be on a regular lattice or a}
\StringTok{          random lattice of points slightly perturbed to minimize aliasing artifacts.}
\StringTok{          samplingPercentage defines the fraction of points to select from the domain. In}
\StringTok{          addition, three point set metrics are available: Euclidean (ICP), Point-set}
\StringTok{          expectation (PSE), and Jensen-Havrda-Charvet-Tsallis (JHCT).}

\StringTok{     -t, --transform Rigid[gradientStep]}
\StringTok{                     Affine[gradientStep]}
\StringTok{                     CompositeAffine[gradientStep]}
\StringTok{                     Similarity[gradientStep]}
\StringTok{                     Translation[gradientStep]}
\StringTok{                     BSpline[gradientStep,meshSizeAtBaseLevel]}
\StringTok{                     GaussianDisplacementField[gradientStep,updateFieldVarianceInVoxelSpace,totalFieldVarianceInVoxelSpace]}
\StringTok{                     BSplineDisplacementField[gradientStep,updateFieldMeshSizeAtBaseLevel,totalFieldMeshSizeAtBaseLevel,<splineOrder=3>]}
\StringTok{                     TimeVaryingVelocityField[gradientStep,numberOfTimeIndices,updateFieldVarianceInVoxelSpace,updateFieldTimeVariance,totalFieldVarianceInVoxelSpace,totalFieldTimeVariance]}
\StringTok{                     TimeVaryingBSplineVelocityField[gradientStep,velocityFieldMeshSize,<numberOfTimePointSamples=4>,<splineOrder=3>]}
\StringTok{                     SyN[gradientStep,updateFieldVarianceInVoxelSpace,totalFieldVarianceInVoxelSpace]}
\StringTok{                     BSplineSyN[gradientStep,updateFieldMeshSizeAtBaseLevel,totalFieldMeshSizeAtBaseLevel,<splineOrder=3>]}
\StringTok{                     Exponential[gradientStep,updateFieldVarianceInVoxelSpace,velocityFieldVarianceInVoxelSpace,<numberOfIntegrationSteps>]}
\StringTok{                     BSplineExponential[gradientStep,updateFieldMeshSizeAtBaseLevel,velocityFieldMeshSizeAtBaseLevel,<numberOfIntegrationSteps>,<splineOrder=3>]}
\StringTok{          Several transform options are available. The gradientStep or learningRate}
\StringTok{          characterizes the gradient descent optimization and is scaled appropriately for}
\StringTok{          each transform using the shift scales estimator. Subsequent parameters are}
\StringTok{          transform-specific and can be determined from the usage. For the B-spline}
\StringTok{          transforms one can also specify the smoothing in terms of spline distance (i.e.}
\StringTok{          knot spacing).}

\StringTok{     -c, --convergence MxNxO}
\StringTok{                       [MxNxO,<convergenceThreshold=1e-6>,<convergenceWindowSize=10>]}
\StringTok{          Convergence is determined from the number of iterations per level and is}
\StringTok{          determined by fitting a line to the normalized energy profile of the last N}
\StringTok{          iterations (where N is specified by the window size) and determining the slope}
\StringTok{          which is then compared with the convergence threshold.}

\StringTok{     -s, --smoothing-sigmas MxNxO...}
\StringTok{          Specify the sigma of gaussian smoothing at each level. Units are given in terms}
\StringTok{          of voxels ('}\NormalTok{vox}\StringTok{') or physical spacing ('}\NormalTok{mm}\StringTok{'). Example usage is '}\NormalTok{4x2x1mm}\StringTok{' and}
\StringTok{          '}\NormalTok{4x2x1vox}\StringTok{' where no units implies voxel spacing.}

\StringTok{     -f, --shrink-factors MxNxO...}
\StringTok{          Specify the shrink factor for the virtual domain (typically the fixed image) at}
\StringTok{          each level.}

\StringTok{     -u, --use-histogram-matching}
\StringTok{          Histogram match the images before registration.}

\StringTok{     -l, --use-estimate-learning-rate-once}
\StringTok{          turn on the option that lets you estimate the learning rate step size only at}
\StringTok{          the beginning of each level. * useful as a second stage of fine-scale}
\StringTok{          registration.}

\StringTok{     -w, --winsorize-image-intensities [lowerQuantile,upperQuantile]}
\StringTok{          Winsorize data based on specified quantiles.}

\StringTok{     -x, --masks [fixedImageMask,movingImageMask]}
\StringTok{          Image masks to limit voxels considered by the metric.}

\StringTok{     --float}
\StringTok{          Use '}\NormalTok{float}\StringTok{' instead of '}\NormalTok{double}\StringTok{' for computations.}
\StringTok{          <VALUES>: 0}

\StringTok{     -v, --verbose (0)/1}
\StringTok{          Verbose output.}

\StringTok{     -h}
\StringTok{          Print the help menu (short version).}

\StringTok{     --help}
\StringTok{          Print the help menu. Will also print values used on the current command line}
\StringTok{          call.}
\end{Highlighting}
\end{Shaded}

\begin{frame}{Template building: creating the average Joe}

\includegraphics{./papers/figures/template0.jpg}

\begin{frame}{``Attractiveness'' \(\rightarrow\) mental processing?}

\includegraphics{./papers/figures/template1.jpg}

\begin{frame}{What about brains?}

\includegraphics{./papers/figures/template3.jpg}

\begin{frame}{Templates facilitate computation}

\includegraphics{./papers/figures/template4.jpg}

\begin{frame}{Gender?}

\includegraphics{./papers/figures/template5.jpg}

\begin{frame}{Nonparametric nonuniform intensity normalization (N3)}

\begin{itemize}
\item
  Developed at the Montreal Neurological Institute (John Sled, 1998)
\item
  Part of the standard preprocessing protocol in large scale projects
  such as ADNI
\item
  The traditional de facto standard in MRI bias correction

  \begin{itemize}
  \tightlist
  \item
    good performance
  \item
    \emph{public availability}
  \end{itemize}
\item
  Public availability --- set of perl scripts coordinating various C++
  programs
\item
  ``\emph{Let's incorporate N3 into ANTs!}''
\end{itemize}

\begin{frame}{Nonparametric nonuniform intensity normalization (N3)}

\includegraphics{./tools/n4/figures/whyN4.png}

\begin{frame}[fragile]{N4 (``Nick's N3'')}

\begin{itemize}
\item
  comparative
  \href{http://www.ncbi.nlm.nih.gov/pubmed/20378467}{evaluation}
\item
  small spline distances (useful for higher magnet strengths)
\item
  multiresolution
\item
  weighted regional mask (used in
  \href{https://github.com/stnava/ANTs/blob/master/Scripts/antsAtroposN4.sh}{\texttt{antsAtroposN4.sh}})
\item
  fast execution times
\item
  \emph{publicly available}
\item
  tested nightly within the ITK dashboard system
\end{itemize}

\begin{frame}{Atropos: flexible code base}

``20+ years of development. \emph{Show me the code!}''

\includegraphics{./tools/atropos/figures/atropos.png}

\begin{frame}{Atropos + N4 \(\rightarrow\) \texttt{antsAtroposN4.sh}}

\includegraphics{./tools/atropos/figures/atroposFlow.png}

\begin{frame}[fragile]{\texttt{DenoiseImage} --- contribution from Jose
Manjon}

\includegraphics{./tools/figures/denoising.png}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{$ }\KeywordTok{DenoiseImage} \NormalTok{--help}

\KeywordTok{COMMAND}\NormalTok{:}
     \KeywordTok{DenoiseImage}
          \KeywordTok{Denoise} \NormalTok{an image using a spatially adaptive filter originally described in J. V.}
          \KeywordTok{Manjon}\NormalTok{, P. Coupe, Luis Marti-Bonmati, D. L. Collins, and M. Robles. Adaptive}
          \KeywordTok{Non-Local} \NormalTok{Means Denoising of MR Images With Spatially Varying Noise Levels,}
          \KeywordTok{Journal} \NormalTok{of Magnetic Resonance Imaging, 31:192-203, June 2010.}

\KeywordTok{OPTIONS}\NormalTok{:}
     \KeywordTok{-d}\NormalTok{, --image-dimensionality 2/3/4}
          \KeywordTok{This} \NormalTok{option forces the image to be treated as a specified-dimensional image. If}
          \KeywordTok{not} \NormalTok{specified, the program tries to infer the dimensionality from the input}
          \KeywordTok{image.}

     \KeywordTok{-i}\NormalTok{, --input-image inputImageFilename}
          \KeywordTok{A} \NormalTok{scalar image is expected as input for noise correction.}

     \KeywordTok{-n}\NormalTok{, --noise-model Rician/(Gaussian)}
          \KeywordTok{Employ} \NormalTok{a Rician or Gaussian noise model.}

     \KeywordTok{-x}\NormalTok{, --mask-image maskImageFilename}
          \KeywordTok{If} \NormalTok{a mask image is specified, denoising is only performed in the mask region.}

     \KeywordTok{-s}\NormalTok{, --shrink-factor (1)}\KeywordTok{/2/3/...}
          \KeywordTok{Running} \NormalTok{noise correction on large images can be time consuming. To lessen}
          \KeywordTok{computation} \NormalTok{time, the input image can be resampled. The shrink factor, specified}
          \KeywordTok{as} \NormalTok{a single integer, describes this resampling. Shrink factor = 1 is the}
          \KeywordTok{default.}

     \KeywordTok{-p}\NormalTok{, --patch-radius 1}
                        \KeywordTok{1x1x1}
          \KeywordTok{Patch} \NormalTok{radius. Default = 1x1x1}

     \KeywordTok{-r}\NormalTok{, --search-radius 3}
                         \KeywordTok{3x3x3}
          \KeywordTok{Search} \NormalTok{radius. Default = 3x3x3.}

     \KeywordTok{-o}\NormalTok{, --output correctedImage}
                  \NormalTok{[}\KeywordTok{correctedImage}\NormalTok{,}\KeywordTok{<}\NormalTok{noiseImage}\KeywordTok{>}\NormalTok{]}
          \KeywordTok{The} \NormalTok{output consists of the noise corrected version of the input image.}
          \KeywordTok{Optionally}\NormalTok{, one can also output the estimated noise image.}

     \KeywordTok{--version}
          \KeywordTok{Get} \NormalTok{Version Information.}

     \KeywordTok{-v}\NormalTok{, --verbose (0)}\KeywordTok{/1}
          \KeywordTok{Verbose} \NormalTok{output.}

     \KeywordTok{-h}
          \KeywordTok{Print} \NormalTok{the help menu (short version)}\KeywordTok{.}

     \KeywordTok{--help}
          \KeywordTok{Print} \NormalTok{the help menu.}
          \KeywordTok{<VALUES>}\NormalTok{: 1}
\end{Highlighting}
\end{Shaded}

\begin{frame}{Multi-atlas segmentation}

\includegraphics{./tools/jointfusion/figures/jointLabelFusion.png}

\begin{frame}{New work: joint intensity fusion}

\includegraphics{./tools/jointfusion/figures/jointIntensityFusion.png}

\begin{frame}{Possible uses}

\begin{itemize}
\item
  ``Correct'' images

  \begin{itemize}
  \item
    motion correction
  \item
    ``remove'' lesions
  \end{itemize}
\item
  Project atlas set intensity signature
\item
  Use in ``corrective learning''
\end{itemize}

@@

@@

\includegraphics{./evaluation/figures/pipeline.png}

>>>>

\documentclass[ignorenonframetext,]{beamer}
\setbeamertemplate{caption}[numbered]
\setbeamertemplate{caption label separator}{: }
\setbeamercolor{caption name}{fg=normal text.fg}
\beamertemplatenavigationsymbolsempty
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\else % if luatex or xelatex
\ifxetex
\usepackage{mathspec}
\else
\usepackage{fontspec}
\fi
\defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
\usetheme{AnnArbor}
\usecolortheme{dolphin}
\usefonttheme{professionalfonts}
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\newif\ifbibliography
\usepackage{longtable,booktabs}
\usepackage{caption}
% These lines are needed to make table captions work with longtable:
\makeatletter
\def\fnum@table{\tablename~\thetable}
\makeatother

@@

\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
\setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}

@@

\title{Quantitative neuroimaging with ANTs}
\author{Nick Tustison}
\date{}

@@

@@

\section{What is ANTs?}\label{what-is-ants}

\begin{frame}{NLM's The Visible Human Project and The Insight Toolkit}

\begin{center}

\includegraphics[width=4.75in]{./figures/VisibleHumanProject_ITK.pdf}

\end{center}

@@

\begin{frame}{ANTs \emph{began with a clinical research need.}}

\begin{center}

\includegraphics[width=4.75in]{./figures/ANTsEvolutionarySummary.pdf}

\end{center}

@@

\begin{frame}{Advanced Normalization Tools}

\begin{center}

\includegraphics[width=4.75in]{./tools/figures/coreANtsToolsNeuro.png}

\end{center}

@@

\begin{frame}{Advanced Normalization Tools \(\rightarrow\) ``ITK-Lung''}

\begin{center}

\includegraphics[width=4.75in]{./tools/figures/coreANtsToolsLung.png}

\end{center}

@@

@@

\scriptsize

@@

\begin{centering}
